Sparse Representation Approaches for First Stage Retrieval: A Review

### 2022-01-08 src/article.tex
Add training paragraph for SPLADE.

>>>>

    \paragraph{Training.}
    The models are initialized with the BERT-base pre-trained models.
    Adam optimizer is selected with the learning rate $2 \cdot 10^{-5}$, linear scheduling,
    a warmup of 6000 steps and a batch size of 124.
    To reduce the contribution of the regularizer in the early stages of training, a planner for
    $\lambda$ is used, which quadratically increases $\lambda$ at each training iteration, up to a
    given step (50k), from which it is fixed for another 100k iterations.
    The hyper-parameter $\lambda$ is chosen from the $[1 \cdot 10^{-4}, 1 \cdot 10^{-1}]$ interval.
